---
title: "End Member Mixing Model"
author: "Jeremy Morris"
date: "8/27/2020"
output: html_document
---

```{r setup, include=FAlSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(broom)
library(purrr)
library(sf)
library(rgdal) # Required for raster I think)
library(tmap)  # plot spatially
library(raster)# make raster
library(gstat) # Use gstat's idw routine
library(sp)    # Used for the spsample functionw

chemdata <- read_csv("C:/Users/jmorris/Desktop/Research/Analysis/Geochemistry/tidy_master.csv") %>% 
  mutate(date = mdy(date)) 

# %>% 
#   gather(-site, -date, - type, key = compound, value = conc_mgl)
```

## Description of Mixing Model

Mass transport equations that require velocity and concentration to determine mix ratio between inputs and resultant mixture. 

For this equation I'll stick to the inputs I've observed ie precip and stream inflow. Try do it for chloride and... 

The math would look like this:

fraction_1 + fraction_2 = 1,

where 1 represents the mixed end member concentration. fraction_1 and fraction_2 are the two constituents that mix to resolve to the observed concentration of the mixed member. using Chloride for the two members we get:
  In mass balance form:
  
Cl_gw = f_crk*Cl_wcrk + f_precip*Cl_precip; 

rearrange to get f_precip = (1 - f_wcrk), and insert back in:

Cl_gw = Cl_wcrk(1 - f_wcrk)+ Cl_precip

f_wcrk = (Cl_gw - Cl_precip)/Cl_wcrk

  
  

#### Setting up the equation:
```{r equation}

mxdat <- chemdata %>% 
  filter(date <= "2019-05-26") %>% 
  filter(site == "a2" & type == "gw" | site == "crk1" | site == "a2" & type == "snow") %>%
  gather(-site,-date,-type,key = compound, value = conc_mgl)%>% 
  dplyr::select(-date,-site) %>% 
  spread(key = type, value = conc_mgl) %>% 
  mutate(frac_gw = (gw - snow)/sfc)







```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FAlSE}
plot(pressure)
```

Note that the `echo = FAlSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
